An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-18 scagnostics.Rmd
Comment added.

Finally, given the results above, it makes sense to also consider smaller parameter-subspaces to look for stronger association. (A procedure to first scout the parameter space for large index values is not efficent in this case because of the strong dependence on rotation angles in this paricular setup.) One subspace for which we found strong association between three variables is using the randomly selected parameter set (m1, ra, chi\_tot, alpha, distance, dec). Optimising again the splines2D index value allows us to find the final view shown in Figure \ref{constructedExample} (left) \textcolor{red}{(The small constribution of alpha is hidden in the axes here, middle plot is without rescaling, therefore same size contribution from dec an alpha to y axis)}, which we can reproduce from the original parameters as shown in the middle, as a combination of the position parameters ra and dec with the spin parameter alpha. For comparison we also show the dependence between ra and dec only, which is fuzzy compared to the ideal view identified by the PP optimisation. \textcolor{red}{This result is unexpected, it can be understood from ?????}

>>>>

Finally, given the results above, it makes sense to also consider smaller parameter-subspaces to look for stronger association. (A procedure to first scout the parameter space for large index values is not efficent in this case because of the strong dependence on rotation angles in this paricular setup.) One subspace for which we found strong association between three variables is using the randomly selected parameter set (m1, ra, chi\_tot, alpha, distance, dec). Optimising again the splines2D index value allows us to find the final view shown in Figure \ref{constructedExample} (left) \textcolor{red}{(The small constribution of alpha is hidden in the axes here, middle plot is without rescaling, therefore same size contribution from dec an alpha to y axis)}, which we can reproduce from the original parameters as shown in the middle, as a combination of the position parameters ra and dec with the spin parameter alpha. For comparison we also show the dependence between ra and dec only, which is fuzzy compared to the ideal view identified by the PP optimisation. \textcolor{red}{This result is unexpected, it can be understood from ????? (Does it mean that knowing the precession angle gives more precise information about the location? Knowing ra uniquely determines dec-alpha rather than dec it seems.)}
